---
title: "Pocillopora Juvenile Fusion"
author: "Ariana Huffmyer (R Markdown author)"
date: "2019"
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_depth: 6
    toc_float: yes
    smart: false
  pdf_document:
    keep_tex: yes
---

## Setup   

Set up workspace, set options, and load required packages. 
```{r, echo=TRUE, show=FALSE}
rm(list=ls(all=TRUE)) 
```

```{r, echo=TRUE, warnings=FALSE}
library(gridExtra)
library(multcomp)
library(emmeans)
library(ggplot2)
library(dplyr)
library(effects)
library(plyr)
library(lattice)
library(glmmTMB)
library(effects)
library(lsmeans)
library(MuMIn)
library(MASS)
library(car)
library(FSA)
library(lmerTest)
library(lme4)
library(blmeco)
library(ggsci)
library(coxme)
library(survival)
library(cowplot)
library(RColorBrewer)
library(tidyverse)
library(partitionBEFsp)
library(factoextra)
library(ggfortify)
library(cowplot)
library(survminer)
```
 
## 1. GROW OUT SURVIVORSHIP  
### **Load data**    

Survivorship is measured as binary on each individual spat in the experiment.    

```{r, results=TRUE}
#load data
rearing<-read.csv("Data/GrowOut_Responses_PostGenotyping.csv", header=TRUE, sep=",", na.strings="NA")
rearing$Quadrant<-as.factor(rearing$Quadrant)
rearing$Diversity.Type<-relevel(rearing$Diversity.Type, ref="Individual")

#rearing$Total.Juveniles<-as.factor(rearing$Total.Juveniles)
#rearing$Fusion.Partners<-as.factor(rearing$Fusion.Partners)
#rearing$Richness<-as.factor(rearing$Richness)
```

Subset the final timepoint for additional analyses.  
```{r, results=TRUE}
final<-rearing[which(rearing$Timepoint == "Final"),]
multiple<-rearing[which(rearing$Community == "Multiple"),]
multiple_final<-multiple[which(multiple$Timepoint == "Final"),]
```

### **Analysis**  

Analyze with a logistic binomial regression model.   

Analyze at the final timepoint.  
```{r, results=TRUE}
#with final dataset
survmod2<-glmer(Survivorship ~ Richness + Community + Fusion.Partners + Richness:Fusion.Partners + (1|Parent.Site/Colony) + (1|Tank) + (1|Slide), data=final, family=binomial)
summary(survmod2)
Anova(survmod2)

#final dataset
summary(effect(c("Richness", "Fusion.Partners"), xlevels=4, survmod2))
summary(effect("Fusion.Partners", xlevels=4, survmod2))
summary(effect("Community", xlevels=4, survmod2))

dispersion_glmer(survmod2) #no overdispersion
plot(residuals(survmod2)) + abline(h=0, lty=2) #Dispersed randomly

```

Create plot for effect of community type.  
```{r, results=TRUE}
eff.surv1 <- predictorEffect("Community", survmod2)
surv.effects1<-plot(eff.surv1,
                   lines=list(multiline=TRUE, 
                              col=c("black"), 
                              lty=1), 
                   confint=list(style="bars", width=4, col="black"), 
                   lwd=4,
                   axes=list(y=list(lim=c(0, 1))),
                   type="response", 
                   ylab=expression(bold("Prob(Survivorship)")), 
                   legend.position="right",
                   xlab=expression(bold("Number of Juveniles")), 
                   main=""); surv.effects1
                   #lattice=list(key.args=list(space="right",
                                              #border=FALSE, 
                                              #title=expression(bold("Genotypic \nRichness")),
                                              #cex=1, 
                                              #cex.title=1)));surv.effects1

```

Create plots for fusion partner effects.  
```{r, results=TRUE}
survmod2a<-glmer(Survivorship ~ Richness + Fusion.Partners + Richness:Fusion.Partners + (1|Parent.Site/Colony) + (1|Tank) + (1|Slide), data=final, family=binomial, subset=c(Community=="Multiple"))

eff.surv2 <- predictorEffect("Fusion.Partners", survmod2a, xlevels=4, rug=TRUE)
surv.effects2<-plot(eff.surv2,
                   lines=list(multiline=TRUE, 
                              col=c("lightblue","mediumblue", "blue4", "darkblue"), 
                              lty=1), 
                   confint=list(style="bands", alpha=0.1), 
                   lwd=4,
                   axes=list(y=list(lim=c(0, 1))),
                   type="response", 
                   ylab=expression(bold("Prob(Survivorship)")), 
                   legend.position="right",
                   xlab=expression(bold("Fusion Partners")), 
                   main="",
                   lattice=list(key.args=list(space="right",
                                              border=FALSE, 
                                              title=expression(bold("Genotypic \nRichness")),
                                              cex=1, 
                                              cex.title=1)));surv.effects2


survmod2b<-glmer(Survivorship ~ Fusion.Partners + (1|Parent.Site/Colony) + (1|Tank) + (1|Slide), data=final, family=binomial, subset=c(Community=="Multiple"))

eff.surv2b <- predictorEffect("Fusion.Partners", survmod2b, xlevels=4, rug=TRUE)
surv.effects2b<-plot(eff.surv2b,
                   lines=list(multiline=TRUE, 
                              col=c("black"), 
                              lty=1), 
                   confint=list(style="bands", alpha=0.1), 
                   lwd=4,
                   axes=list(y=list(lim=c(0, 1))),
                   type="response", 
                   ylab=expression(bold("Prob(Survivorship)")), 
                   legend.position="right",
                   xlab=expression(bold("Fusion Partners")), 
                   main="",
                   lattice=list(key.args=list(space="none",
                                              border=FALSE, 
                                              title=expression(bold("")),
                                              cex=1, 
                                              cex.title=1)));surv.effects2b
```

Generate mean values of survivorship for 1) number of juveniles and 2) within "multiple" juvenile groups, mean values for number of fusion partners.   
```{r, results=TRUE}

meansurv <- ddply(final, c("Community"), summarise,
                   N    = length(Survivorship[!is.na(Survivorship)]),
                   mean = mean(Survivorship, na.rm=TRUE),
                   sd   = sd(Survivorship, na.rm=TRUE),
                   se   = sd / sqrt(N), 
                   max = max(Survivorship, na.rm=TRUE),
                   lower = mean-sd, 
                   upper = mean+sd
                   )
meansurv

meansurv2 <- ddply(multiple_final, c("Fusion.Partners"), summarise,
                   N    = length(Survivorship[!is.na(Survivorship)]),
                   mean = mean(Survivorship, na.rm=TRUE),
                   sd   = sd(Survivorship, na.rm=TRUE),
                   se   = sd / sqrt(N), 
                   max = max(Survivorship, na.rm=TRUE),
                   lower = mean-sd, 
                   upper = mean+sd
                   )
meansurv2

meansurv3 <- ddply(multiple_final, c("Richness"), summarise,
                   N    = length(Survivorship[!is.na(Survivorship)]),
                   mean = mean(Survivorship, na.rm=TRUE),
                   sd   = sd(Survivorship, na.rm=TRUE),
                   se   = sd / sqrt(N), 
                   max = max(Survivorship, na.rm=TRUE),
                   lower = mean-sd, 
                   upper = mean+sd
                   )
meansurv3

```

## 2. GROW OUT FUSION

### **Analysis**    

Analyze with a logistic binomial regression model.  

Final timepoint dataset. 

Analyze fusion as a product of genotypic richness within "multiple" juvenile groups.   
```{r, results=FALSE}
#with final dataset
fusemod1<-glmer(Fusion ~ Richness + (1|Parent.Site/Colony) + (1|Tank) + (1|Slide), data=final, family=binomial, subset=c(Community=="Multiple"))
summary(fusemod1)
Anova(fusemod1, type="II") # no effects on rate of fusion by the end point

dispersion_glmer(fusemod1) #no overdispersion
plot(residuals(fusemod1)) + abline(h=0, lty=2)
```

There is an effect of genotypic diversity on fusion rates. Plot the relationship.   
```{r, results=TRUE}
eff.fuse1 <- predictorEffect("Richness", fusemod1, xlevels=4, rug=TRUE)
fuse.effects1<-plot(eff.fuse1,
                   lines=list(multiline=TRUE, 
                              col=c("black"), 
                              lty=1),
                   confint=list(style="bands", alpha=0.1), 
                   lwd=4,
                   #axes=list(y=list(lim=c(0, 1))),
                   type="response", 
                   ylab=expression(bold("Prob(Successful Fusion)")), 
                   xlab=expression(bold("Richness")), 
                   main="",
                   lattice=list(key.args=list(space="right",
                                              border=FALSE, 
                                              title=expression(bold("Genotypic \nRichness")),
                                              cex=1, 
                                              cex.title=1)));fuse.effects1
```

Generate a summary of proportion fused at the end of the grow-out period.  

```{r, results=TRUE}
meanfusion <- ddply(multiple_final, c("Richness"), summarise,
                   N    = length(Fusion[!is.na(Fusion)]),
                   mean = mean(Fusion, na.rm=TRUE),
                   sd   = sd(Fusion, na.rm=TRUE),
                   se   = sd / sqrt(N), 
                   max = max(Fusion, na.rm=TRUE),
                   lower = mean-sd, 
                   upper = mean+sd
                   )
meanfusion

```


## 3. GROW OUT GROWTH  
### **Analysis**  

Growth is measured as polyp expansion in each spat by number of spat in each sibling type and number of fused individuals. Growth is measured in final dataset as all spat started with 1 polyp each.    

Analyze polyp expansion with the final dataset and present means.      
 
```{r, results=TRUE}
polypmod1<-glmer(Polyps ~ Richness + Community + Fusion.Partners + Richness:Fusion.Partners + (1|Parent.Site/Colony) + (1|Tank) + (1|Slide), data=final, family = poisson)
summary(polypmod1)
Anova(polypmod1, type="II")
qqPlot(residuals(polypmod1))

meangrowth <- ddply(final, c("Community"), summarise,
                   N    = length(Polyps[!is.na(Polyps)]),
                   mean = mean(Polyps, na.rm=TRUE),
                   sd   = sd(Polyps, na.rm=TRUE),
                   se   = sd / sqrt(N), 
                   max = max(Polyps, na.rm=TRUE),
                   lower = mean-sd, 
                   upper = mean+sd
                   )
meangrowth

```

Plot the model outputs.  

```{r, results=TRUE}
eff.polyps1 <- predictorEffect("Fusion.Partners", polypmod1, xlevels=4, rug=TRUE)
polyp.effects1<-plot(eff.polyps1,
                   lines=list(multiline=TRUE, 
                              col=c("lightblue","mediumblue", "blue4", "darkblue"), 
                              lty=1), 
                   confint=list(style="bands", alpha=0.1), 
                   lwd=4,
                   #axes=list(y=list(lim=c(0, 1))),
                   type="response", 
                   ylab=expression(bold("Total Polyp Expansion")), 
                   legend.position="right",
                   xlab=expression(bold("Fusion Partners")), 
                   main="",
                   lattice=list(key.args=list(space="right",
                                              border=FALSE, 
                                              title=expression(bold("Genotypic \nRichness")),
                                              cex=1, 
                                              cex.title=1)));polyp.effects1
```


Combine figures for Grow-Out Period.  
```{r, results=TRUE}
grow_out_figs<-plot_grid(surv.effects1, surv.effects2b, labels = c("A", "B"), ncol=2, nrow=1, rel_heights= c(1,1), rel_widths = c(0.8,1), label_size = 20, label_y=1, align="h");grow_out_figs

ggsave(filename="Figures/grow_out_figs.png", plot=grow_out_figs, dpi=500, width=10, height=6, units="in")
```


## 4. STRESS SURVIVORSHIP
### **Load data**     

Survivorship is measured as binary on each individual spat in the experiment.  
 
```{r, results=TRUE}
#load data
stress<-read.csv("Data/Stress_Responses_PostGenotyping.csv", header=TRUE, sep=",", na.strings="NA")
stress$Diversity.Type<-relevel(stress$Diversity.Type, ref="Individual")
stress$Polyps<-as.numeric(stress$Polyps)
stress$Fusion.Type<-relevel(stress$Fusion.Type, ref="Not Fused")
stress$Richness.Type<-relevel(stress$Richness.Type, ref="Single")

#remove non-fused from analysis 
stressdrop<-droplevels(stress[!stress$Fusion.Type == 'Not Fused',])
``` 

Subset the final timepoint, "multiple" juvenile datasets for additional analyses.  
```{r, results=FALSE}
final_stress<-stress[which(stress$Timepoint == "End"),]
final_stress_drop<-stressdrop[which(stressdrop$Timepoint == "End"),]
multiple_stress<-stress[which(stress$Community == "Multiple"),]
multiple_final_stress<-multiple_stress[which(multiple_stress$Timepoint == "End"),]
multiple_d26_stress<-multiple_stress[which(multiple_stress$Timepoint == "S2D11"),]
d26_stress<-stress[which(stress$Timepoint == "S2D11"),]
d23_stress<-stress[which(stress$Timepoint == "S2D8"),]
``` 

### **Analysis**  

Analyze with a logistic binomial regression model.  

Analyze survivorship during the stress test as survivorship as a function of fusion status and genotypic richness. Fusion is classified as "Fused" or "Not Fused" at the beginning of the stress test. Genotypic richness is classified as "single" genotype or "multiple" genotypes. This is to maximize sample size due to mortality and low sample size within levels of fusion partners and genotypic richness. Individuals are referred to as "individuals". 

First, examine sample size of groups. As there were very few "not fused" individuals in multiple juvenile slides, these will be removed from the analysis. We will only analyze survivorship of "individuals" and those which are "fused". We will then examine the differences between "single" and "multiple" genotype groups.  

```{r, results=TRUE}
meanstresssurv1 <- ddply(stress, c("Fusion.Type", "Diversity.Type", "Day", "Treatment"), summarise,
                   N    = length(Survivorship[!is.na(Survivorship)]),
                   mean = mean(Survivorship, na.rm=TRUE),
                   sd   = sd(Survivorship, na.rm=TRUE),
                   se   = sd / sqrt(N), 
                   max = max(Survivorship, na.rm=TRUE),
                   lower = mean-sd, 
                   upper = mean+sd
                   )
meanstresssurv1
```

Display means with the not fused group removed.  

```{r, results=TRUE}

meanstresssurv2 <- ddply(stressdrop, c("Fusion.Type", "Diversity.Type", "Day", "Treatment"), summarise,
                   N    = length(Survivorship[!is.na(Survivorship)]),
                   mean = mean(Survivorship, na.rm=TRUE),
                   sd   = sd(Survivorship, na.rm=TRUE),
                   se   = sd / sqrt(N), 
                   max = max(Survivorship, na.rm=TRUE),
                   lower = mean-sd, 
                   upper = mean+sd
                   )
meanstresssurv2
```

Now that the "not fused" group is removed, analyze the effect of richness, fusion, and treatment on survivorship over the course of the stress test. Note that there is no interaction between richness type and fusion type as individual juveniles are not exposed to other juveniles and therefore no option for genotypic richness.  

```{r, results=TRUE}
stressmod1<-glmer(Survivorship ~ Day + Treatment + Fusion.Type + Richness.Type + Day:Treatment + Day:Fusion.Type + Day:Richness.Type + Day:Treatment:Fusion.Type + Day:Treatment:Richness.Type + Treatment:Fusion.Type + Treatment:Richness.Type + (1|Parent.Site/Colony) + (1|Treatment:Tank) + (1|Slide), data=stressdrop, family=binomial, link=logit) 

summary(stressmod1)
Anova(stressmod1, type="II")
dispersion_glmer(stressmod1) #no overdispersion
```

There is a significant interaction between treatment and fusion as well as treatment and richness First plot the effect of fusion.  

```{r, results=TRUE}
#generate model for effect plot  
stressdrop$group<-paste(stressdrop$Treatment, "-", stressdrop$Fusion.Type)

stressmod2<-glmer(Survivorship ~ Day * group + (1|Parent.Site/Colony) + (1|Treatment:Tank) + (1|Slide), data=stressdrop, family=binomial, link=logit) 

eff.stress2 <- predictorEffect(c("Day"), stressmod2)

stress.effectsFUSE<-plot(eff.stress2,
                   lines=list(multiline=TRUE, 
                              col=c("blue", "blue", "red", "red"), 
                              lty=c(2,1,2,1)), 
                   confint=list(style="bands", alpha=0.1), 
                   lwd=4,
                   axes=list(y=list(lim=c(0, 1.1))),
                   type="response", 
                   ylab=expression(bold("Prob(Survivorship)")), 
                   legend.position="top",
                   xlab=expression(bold("Day")), 
                   main="",
                   lattice=list(key.args=list(space="top",
                                              border=FALSE, 
                                              title=expression(bold("Temperature - Fusion")),
                                              cex=1, 
                                              cex.title=1)));stress.effectsFUSE
```

Obtain effect summary for effects of fusion.  

```{r, results=TRUE}
summary(effect(c("Day", "group"), xlevels=50, stressmod2))
```

The curves for high temperature meet 50% at the following timepoints:  

High individual = ~ 20.4 days   
High fused = ~ 25.5 days   

50% mortality (LT50) is approximately 5 days later for fused corals than for individuals in this stress test.  

Next plot the effect of genotypic richness within the fused corals.  

```{r, results=TRUE}
stressdrop$group<-paste(stressdrop$Treatment, "-", stressdrop$Richness.Type)

stressmod3<-glmer(Survivorship ~ Day * group + (1|Parent.Site/Colony) + (1|Treatment:Tank) + (1|Slide), data=stressdrop, family=binomial, link=logit, subset=c(Fusion.Type=="Fused")) 

eff.stress3 <- predictorEffect(c("Day"), stressmod3)
stress.effectsRICHNESS<-plot(eff.stress3,
                   lines=list(multiline=TRUE, 
                              col=c("blue", "blue", "red", "red"), 
                              lty=c(2,1,2,1)), 
                   confint=list(style="bands", alpha=0.1), 
                   lwd=4,
                   axes=list(y=list(lim=c(0, 1.1))),
                   type="response", 
                   ylab=expression(bold("Prob(Survivorship)")), 
                   legend.position="top",
                   xlab=expression(bold("Day")), 
                   main="",
                   lattice=list(key.args=list(space="top",
                                              border=FALSE, 
                                              title=expression(bold("Temperature - Genotypic Richness")),
                                              cex=1, 
                                              cex.title=1)));stress.effectsRICHNESS
```

Obtain effect summary for effects of richness.  

```{r, results=TRUE}
summary(effect(c("Day", "group"), xlevels=50, stressmod3))
```

The curves for high temperature meet 50% at the following timepoints:  

High multiple = ~ 26 days   
High single = ~ 24.5 days   

50% mortality (LT50) is approximately 1.5 days later for multiple genotype fusions than for single genotype fusions in this stress test.  


## 5. STRESS FUSION  

### **Analysis**    
 
Analyze with a logistic binomial regression model.      

Analyze fusion success by the end of the stress test within fused corals by treatment and genotypic richness.     

```{r, results=FALSE}
stressfuse1<-glmer(Fusion ~ Treatment * Richness.Type + (1|Parent.Site/Colony) + (1|Treatment:Tank) + (1|Slide), data=final_stress_drop, family=binomial, link=logit, subset=c(Fusion.Type=="Fused")) 

summary(stressfuse1)
Anova(stressfuse1, type="II") 

plot(allEffects(stressfuse1))

dispersion_glmer(stressfuse1) #no overdispersion

```


```{r, results=TRUE}
meanstressfuse <- ddply(final_stress_drop, c("Treatment", "Richness.Type"), summarise,
                   N    = length(Fusion[!is.na(Fusion)]),
                   mean = mean(Fusion, na.rm=TRUE),
                   sd   = sd(Fusion, na.rm=TRUE),
                   se   = sd / sqrt(N), 
                   max = max(Fusion, na.rm=TRUE),
                   lower = mean-sd, 
                   upper = mean+sd
                   )
meanstressfuse
```

There is no effect of treatment or richness on fusion sucess. There is a trend for slightly lower fusion in high temperature, but this was not significant.       

## 6. STRESS GROWTH  
 
Analyze with a poisson regression model.     

Analyze growth as polyp expansion at day 23 of 32 of the stress test. Due to high mortality, this is the last time point with suffficient sample size to measure growth.   

Display mean values. Day 23 has sufficient sample size.    

```{r, results=TRUE}
meanstressgrowth <- ddply(stressdrop, c("Day", "Treatment", "Fusion.Type", "Richness.Type"), summarise,
                   N    = length(Polyps[!is.na(Polyps)]),
                   mean = mean(Polyps, na.rm=TRUE),
                   sd   = sd(Polyps, na.rm=TRUE),
                   se   = sd / sqrt(N), 
                   max = max(Polyps, na.rm=TRUE),
                   lower = mean-sd, 
                   upper = mean+sd
                   )
meanstressgrowth
```

Analyze the effect of temperature, fusion, and genotypic richness on polyp expansion at day 23.  

```{r, results=TRUE}
stresspolypmod1<-glmer(Polyps ~ Treatment + Richness.Type + Fusion.Type + Treatment:Richness.Type + Treatment:Fusion.Type + (1|Parent.Site/Colony) + (1|Treatment:Tank) + (1|Slide), data=stressdrop, family = poisson, subset=c(Timepoint=="S2D8"))

summary(stresspolypmod1)
Anova(stresspolypmod1, type="II")
qqPlot(residuals(stresspolypmod1))
``` 

There is no effect of treatment, fusion or genotypic richness on growth. Treatment is near significant at p=0.0525.  

Generate a plot of polyp expansion by temperature treatment.    

```{r, results=TRUE}
stresspolypmod2<-glmer(Polyps ~ Treatment + (1|Parent.Site/Colony) + (1|Treatment:Tank) + (1|Slide), data=stressdrop, family = poisson, subset=c(Timepoint=="S2D8"))
summary(stresspolypmod2)
Anova(stresspolypmod2, type="II")

eff.stress.polyps1 <- predictorEffect("Treatment", stresspolypmod2)
polyps.stress.effects1<-plot(eff.stress.polyps1,
                   lines=list(multiline=TRUE, 
                              col=c("black"), 
                              lty=1), 
                   confint=list(style="bars", width=4, col="black"), 
                   lwd=4,
                   axes=list(y=list(lim=c(5,8))),
                   type="response", 
                   ylab=expression(bold("Polyp Expansion")), 
                   legend.position="right",
                   xlab=expression(bold("Temperature")), 
                   main=""); polyps.stress.effects1
                   #lattice=list(key.args=list(space="right",
                                              #border=FALSE, 
                                              #title=expression(bold("Genotypic \nRichness")),
                                              #cex=1, 
                                              #cex.title=1)));surv.effects1
```

Combine figures for Stress Period:  

```{r, results=TRUE}
stress_figs<-plot_grid(stress.effectsFUSE, stress.effectsRICHNESS, labels = c("A", "B"), ncol=2, nrow=1, rel_heights= c(1,1), rel_widths = c(1,1), label_size = 20, label_y=1, align="h");stress_figs

ggsave(filename="Figures/stress_figs.png", plot=stress_figs, dpi=500, width=20, height=6, units="in")
```
 

## 7. TEMPERATURE DATA

Load in temperature data from Apex files. Data were recorded every 15 minutes and probes were calibrated to a digital thermometer weekly.     
 
```{r, restults=TRUE}
juvtemps<-read.csv("Data/ApexTemps.csv", header=T, na.strings="NA")
#convert Date and Time to date/time format
juvtemps$Date <- as.POSIXct(juvtemps$Date, format="%m/%d/%y %H:%M")

#convert to long format
juvtemps<-juvtemps %>% gather(Tank, Temperature, Tank17:Tank24)
juvtemps$Tank<-as.factor(juvtemps$Tank)

dailymax<-juvtemps[which(juvtemps$TimeDay == "930"),]
dailymax<-juvtemps[which(juvtemps$Phase == "Stress"),]

dailymax$Treatment<-ifelse(dailymax$Tank %in% c("Tank17"), "Ambient",
                            ifelse(dailymax$Tank %in% c("Tank18"), "Ambient", 
                            ifelse(dailymax$Tank %in% c("Tank19"), "High",
                            ifelse(dailymax$Tank %in% c("Tank20"), "High",
                            ifelse(dailymax$Tank %in% c("Tank21"), "Ambient",
                            ifelse(dailymax$Tank %in% c("Tank22"), "High",
                            ifelse(dailymax$Tank %in% c("Tank23"), "Ambient",
                            ifelse(dailymax$Tank %in% c("Tank24"), "High",NA))))))))

maxtemps <- ddply(dailymax, c("Treatment"), summarise,
                   N    = length(Temperature[!is.na(Temperature)]),
                   mean = mean(Temperature, na.rm=TRUE),
                   sd   = sd(Temperature, na.rm=TRUE),
                   se   = sd / sqrt(N), 
                   max = max(Temperature, na.rm=TRUE),
                   lower = mean-sd, 
                   upper = mean+sd
                   )

juvtemps$Period<-ifelse(juvtemps$Phase %in% c("Stress"), "Stress",
                            ifelse(juvtemps$Phase %in% c("Stress2"), "Stress", 
                            ifelse(juvtemps$Phase %in% c("Acclimation"), "Stress",
                            ifelse(juvtemps$Phase %in% c("Hurricane"), "Hurricane",
                            ifelse(juvtemps$Phase %in% c("Ambient"), "Grow-Out",NA)))))


```

Plot timeseries of temperature data with tank temperature in colors.   

```{r, results=TRUE}
#subset temperature measurements

juvtempsHIGH<-subset(juvtemps, Period==c("Stress"), c(Date, TimeDay, Phase, Tank, Temperature, Period))
juvtempsHIGH$Treatment<-ifelse(juvtempsHIGH$Tank %in% c("Tank17"), "Ambient",
                            ifelse(juvtempsHIGH$Tank %in% c("Tank18"), "Ambient", 
                            ifelse(juvtempsHIGH$Tank %in% c("Tank19"), "High",
                            ifelse(juvtempsHIGH$Tank %in% c("Tank20"), "High",
                            ifelse(juvtempsHIGH$Tank %in% c("Tank21"), "Ambient",
                            ifelse(juvtempsHIGH$Tank %in% c("Tank22"), "High",
                            ifelse(juvtempsHIGH$Tank %in% c("Tank23"), "Ambient",
                            ifelse(juvtempsHIGH$Tank %in% c("Tank24"), "High",NA))))))))

juvtempsHURR<-subset(juvtemps, Period==c("Hurricane"), c(Date, TimeDay, Phase, Tank, Temperature, Period))
juvtempsHURR$Treatment<-ifelse(juvtempsHURR$Tank %in% c("Tank17"), "Ambient",
                            ifelse(juvtempsHURR$Tank %in% c("Tank18"), "Ambient", 
                            ifelse(juvtempsHURR$Tank %in% c("Tank19"), "High",
                            ifelse(juvtempsHURR$Tank %in% c("Tank20"), "High",
                            ifelse(juvtempsHURR$Tank %in% c("Tank21"), "Ambient",
                            ifelse(juvtempsHURR$Tank %in% c("Tank22"), "High",
                            ifelse(juvtempsHURR$Tank %in% c("Tank23"), "Ambient",
                            ifelse(juvtempsHURR$Tank %in% c("Tank24"), "High",NA))))))))

juvtempsGROW<-subset(juvtemps, Period==c("Grow-Out"), c(Date, TimeDay, Phase, Tank, Temperature, Period))
juvtempsGROW$Treatment<-ifelse(juvtempsGROW$Tank %in% c("Tank17"), "Ambient",
                            ifelse(juvtempsGROW$Tank %in% c("Tank18"), "Ambient", 
                            ifelse(juvtempsGROW$Tank %in% c("Tank19"), "Ambient",
                            ifelse(juvtempsGROW$Tank %in% c("Tank20"), "Ambient",
                            ifelse(juvtempsGROW$Tank %in% c("Tank21"), "Ambient",
                            ifelse(juvtempsGROW$Tank %in% c("Tank22"), "Ambient",
                            ifelse(juvtempsGROW$Tank %in% c("Tank23"), "Ambient",
                            ifelse(juvtempsGROW$Tank %in% c("Tank24"), "Ambient",NA))))))))

juvtemps<-rbind(juvtempsHIGH, juvtempsGROW)
juvtemps<-rbind(juvtemps, juvtempsHURR)

TimeSeries1j<-ggplot(juvtemps, aes(x = Date, y = Temperature)) + 
  geom_line(aes(color = Treatment), size = 1) +
  scale_color_manual(values=c("blue", "red")) +
  ylab("Temperature (°C)")+
  xlab("Date")+
  ylim(26,32)+
  geom_vline(xintercept = as.POSIXct(as.Date(c("2018-07-31 10:00:00"))), linetype="solid", 
                color = "black", size=1)+
  geom_vline(xintercept = as.POSIXct(as.Date(c("2018-08-16 00:00:00"))), linetype="dashed", 
                color = "black", size=1)+
  geom_vline(xintercept = as.POSIXct(as.Date(c("2018-09-20 16:00:00"))), linetype="dotted", 
                color = "black", size=1)+
  theme_classic()+
  scale_x_datetime(limits = as.POSIXct(as.Date(c("2018-07-30 09:00:00", "2018-09-20 21:00:00")))) +
  theme(legend.position="none")+
  theme(text = element_text(size = 18, color="black"))+
  theme(axis.text = element_text(size=16, color="black"));TimeSeries1j
```


Plot by time of day by summarizing the mean temp at each time of day for each tank. Display the mean temperatures of each treatment during the Stress test phase (excluding the pause in treatment due to the hurricane system shutdown).     

```{r, results=FALSE}
#subset juv temps for the stress period
juvtempsSTRESS<-juvtemps
juvtempsSTRESS$Period<-ifelse(juvtempsSTRESS$Phase %in% c("Stress"), "Stress",
                            ifelse(juvtempsSTRESS$Phase %in% c("Stress2"), "Stress", 
                            ifelse(juvtempsSTRESS$Phase %in% c("Acclimation"), "Acclimation",
                            ifelse(juvtempsSTRESS$Phase %in% c("Hurricane"), "Hurricane",
                            ifelse(juvtempsSTRESS$Phase %in% c("Ambient"), "Grow-Out",NA)))))

juvtempsSTRESS

juvtempsSTRESS<-juvtempsSTRESS[which(juvtempsSTRESS$Phase == "Stress"),]


QuarterlyJ <- ddply(juvtempsSTRESS, c("TimeDay", "Treatment"), summarise,
                   N    = length(Temperature[!is.na(Temperature)]),
                   mean = mean(Temperature, na.rm=TRUE),
                   sd   = sd(Temperature, na.rm=TRUE),
                   se   = sd / sqrt(N), 
                   max = max(Temperature, na.rm=TRUE),
                   lower = mean-sd, 
                   upper = mean+sd
                   )

MeansJtemp <- ddply(juvtemps, c("Period", "Treatment"), summarise,
                   N    = length(Temperature[!is.na(Temperature)]),
                   mean = mean(Temperature, na.rm=TRUE),
                   sd   = sd(Temperature, na.rm=TRUE),
                   se   = sd / sqrt(N)
                   )
MeansJtemp

MeansJtemp2 <- ddply(juvtemps, c("Treatment"), summarise,
                   N    = length(Temperature[!is.na(Temperature)]),
                   mean = mean(Temperature, na.rm=TRUE),
                   max = max(Temperature, na.rm=TRUE),
                   sd   = sd(Temperature, na.rm=TRUE),
                   se   = sd / sqrt(N)
                   )
MeansJtemp2
```

Generate final figure.  

```{r, results=TRUE}
JuvTempsDay<-ggplot(QuarterlyJ, aes(x = TimeDay, y = mean, color=Treatment, fill=Treatment)) + 
  geom_line(color="black", size = 1) +
  #facet_wrap(~Period) +
  scale_x_continuous(breaks=c(0, 720, 1440), labels=c("0:00", "12:00", "24:00")) +
  scale_color_manual(values = c("blue", "red")) +
  scale_fill_manual(values = c("blue", "red")) +
  theme_classic() +
  geom_ribbon(aes(ymin=QuarterlyJ$lower, ymax=QuarterlyJ$upper), linetype=2, alpha=0.4, color=NA) +
  ylab("Temperature (°C)") +
  xlab("Time of Day") +
  ylim(26,32)+
  theme(text = element_text(size = 18, color="black"))+
  theme(panel.margin = unit(2, "lines"))+
  theme(axis.text = element_text(size=16, color="black")); JuvTempsDay
```


Combine figures for temperature.  
```{r, results=TRUE}
temp_figs<-plot_grid(TimeSeries1j, JuvTempsDay, labels = c("A", "B"), ncol=2, nrow=1, rel_heights= c(1,1), rel_widths = c(1,0.8), label_size = 20, label_y=1, align="h");temp_figs

ggsave(filename="Figures/temp_figs.png", plot=temp_figs, dpi=500, width=14, height=6, units="in")
```

